---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mypkgr

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/Florian-40/mypkgr.svg?branch=master)](https://travis-ci.com/Florian-40/mypkgr)
<!-- badges: end -->

The goal of mypkgr is to calculate values of multivariate gaussian density and learning how to build R package. 

## Installation

You can install the development version of `mypkgr` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Florian-40/mypkgr")
```

## Example

This is a basic example which shows you how to solve a common problem:

### Univariate density 
```{r example}
library(mypkgr)
mvnpdf(x=matrix(c(1.96,-0.5), ncol=2), Log=FALSE)
```

### Bivariate density
```{r}
mvnpdf(x=matrix(rep(1.96,2),nrow=2, ncol=1),Log=FALSE)
```

### Graphical representation.
```{r}
pdfvalues <- mvnpdf(x=matrix(seq(-3,3, by=0.1), nrow=1), Log=FALSE)
plot(pdfvalues)
```

## `C++`functions. 

To use `C++` function, we use the code below : 
```{r}
Rcpp::sourceCpp("src/timesTwo.cpp")
timesTwo(12.5)
```

And for inversion matrix : 
```{r}
Rcpp::sourceCpp("src/invC.cpp")
A<-matrix(c(2,4,7,8,9,5,6,5,4), nrow=3, ncol=3)
invC(A)
```


