---
title: "Comparaison des temps d'execution."
output: 
  rmarkdown::html_vignette: 
vignette: >
  %\VignetteIndexEntry{Execution times.}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup }
library(mypkgr)
library(microbenchmark)
library(ggplot2)
```

## Comparison with our microbenchmark package.

You can find microbenchmark package on my Git-Hub page : <https://github.com/Florian-40/microbenchmark.git>


```{r}
mb <- microbenchmark(mvtnorm::dmvnorm(rep(1.96, 2)),
                     mvnpdf(x=matrix(rep(1.96,2)), Log=FALSE),
                     times=1000L)

mb
expression<-c('dmvnorm', 'mvnpdf')
autoplot(mb, expression)
```

And with multidimensionnal, we get :
```{r}
n <- 100
mb <- microbenchmark(mvtnorm::dmvnorm(matrix(1.96, nrow = n, ncol = 2)),
                     mvnpdf(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     times=100L)
mb
expression<-c('dmvnorm', 'mvnpdf')
autoplot(mb, expression)
```


## Profiling

By using this lines in terminal, we can check profiling of the code : 
```{r, eval=FALSE}
profvis::profvis({
+ n <- 10e4
+ pdfval <- mvnpdf(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE)
+ })
```

### `mvnpdfsmart`function.

We can use new function `mvnpdfmart` and check profile with similar code : 
```{r, eval=FALSE}
profvis::profvis({
+ n <- 10e4
+ pdfval <- mvnpdfsmart(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE)
+ })
```

We can compare results with a `microbenchmark` :
```{r}
n <- 1000
mb <- microbenchmark(mvtnorm::dmvnorm(matrix(1.96, nrow = n, ncol = 2)),
                     mvnpdf(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdfsmart(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     times=100L)
mb
expression<-c('dmvnorm', 'mvnpdf', 'mvnpdfsmart')
autoplot(mb, expression)
```

### `mvnpdfoptim` function. 

We can use new function `mvnpdfmart` and check profile with similar code : 
```{r, eval=FALSE}
profvis::profvis({
+ n <- 10e4
+ pdfval <- mvnpdfoptim(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE)
+ })
```

We can compare all results with a `microbenchmark`:
```{r}
n <- 1000
mb <- microbenchmark(mvtnorm::dmvnorm(matrix(1.96, nrow = n, ncol = 2)),
                     mvnpdf(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdfsmart(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdfoptim(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     times=100L)
mb
expression<-c('dmvnorm', 'mvnpdf', 'mvnpdfsmart', 'mvnpdfoptim')
autoplot(mb, expression)
```

## Using Rccp Armadillo functions. 

We write a better inversion matrix with C++ language and we include it in `mvnpdfsmart`. Thus, we get microbenchmark : 
```{r}
n <- 1000
mb <- microbenchmark(mvtnorm::dmvnorm(matrix(1.96, nrow = n, ncol = 2)),
                     mvnpdf(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdfsmart(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdfoptim(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdf_invC(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     times=100L)
mb
expression<-c('dmvnorm', 'mvnpdf', 'mvnpdfsmart', 'mvnpdfoptim', 'mvnpdf_invC')
autoplot(mb, expression)
```

Now, use complete implementation of `mvnpdfsmart` in C++.


```{r}
Rcpp::sourceCpp("../src/mvnpdfC.cpp")
n <- 1000
mb <- microbenchmark(mvtnorm::dmvnorm(matrix(1.96, nrow = n, ncol = 2)),
                     mvnpdf(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdfsmart(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdfoptim(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdf_invC(x=matrix(1.96, nrow = 2, ncol = n), Log=FALSE),
                     mvnpdfC(x=matrix(1.96, nrow = 2, ncol = n), mean = rep(0, 2), varcovM = diag(2), Log=FALSE),
                     times=100L)
mb
expression<-c('dmvnorm', 'mvnpdf', 'mvnpdfsmart', 'mvnpdfoptim', 'mvnpdf_invC', 'mvnpdfC')
autoplot(mb, expression)
```

## Parallel code

### 1st simple example. 

Let's try to calculate the logarithm of $n$ numbers. 

```{r}
mb <- microbenchmark(log_par(1:100), log_seq(1:100), times=50)
mb
expression <- c('log_par', 'log_seq')
autolplot(mb)
```




